Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-22 doc/manuscript/manuscript.Rmd
add sclerotinia report references

<!-- Most of the previous studies on *S. sclerotiorum* had been conducted in the USA, Canada and Australia but not in Europe. 
In those studies, different dry bean cultivars had been rarely used as  hosts to investigate any host-pathogen relationships or specificity.
No white mold resistant dry bean cultivars exist.
Canopy architecture and growth pattern of some cultivars enable improved disease avoidance [@kolkman2002agronomic]. -->
To date, no commercial white mold-resistant dry bean cultivars exist. 
Field trials in some regions of the US have shown the G122 cultivar is partially resistant while the Beryl cultivar is susceptible [@otto-hanson2011variation; @steadman2004identification].

@@

In this study, we analyze and characterize the genetic and phenotypic diversity of 366 *S. sclerotiorum* isolates collected between 2003 and 2012 from dry bean cultivars among different geographic locations in the United States, France, Mexico, and Australia. 
Because the white mold nurseries serve as testing grounds for new varieties of dry bean, we wanted to know if the *S. sclerotiorum* populations from white mold nurseries were representative of the fields within the same region. 
As these nurseries are not treated with any chemical or cultural control of white mold, we hypothesized that these nurseries would represent the natural population of *S. sclerotiorum*.
Furthermore, as three cultivars (Beryl, Bunsi, and G122) were grown among all white mold nurseries, we wanted to investigate the potential effect of cultivar on genetic diversity.
We additionally wanted to assess what categorical or phenotypic variables best predict genetic structure and if there was correlation between multilocus genotype and mycelial compatibility group.
By investigating these aims, we hope to effectively describe the population dynamics of *S. sclerotiorum* and make available our database of isolates for use in future dry bean breeding efforts.

>>>>

<!-- Most of the previous studies on *S. sclerotiorum* had been conducted in the USA, Canada and Australia but not in Europe. 
In those studies, different dry bean cultivars had been rarely used as  hosts to investigate any host-pathogen relationships or specificity.
No white mold resistant dry bean cultivars exist.
Canopy architecture and growth pattern of some cultivars enable improved disease avoidance [@kolkman2002agronomic]. -->
To date, no commercial white mold-resistant dry bean cultivars exist. 
Field trials in some regions of the US have shown the G122 cultivar is partially resistant while the Beryl cultivar is susceptible [@otto-hanson2011variation; @steadman2004identification].
<!-- This puny paragraph needs a lot of work to more fully describe the operation of the wmn -->

@@

In this study, we analyze and characterize the genetic and phenotypic diversity of 366 *S. sclerotiorum* isolates collected between 2003 and 2012 from dry bean cultivars among different geographic locations in the United States, France, Mexico, and Australia. 
Because the white mold nurseries serve as testing grounds for new varieties of dry bean, we wanted to know if the *S. sclerotiorum* populations from white mold nurseries were representative of the fields within the same region. 
As these nurseries are not treated with any chemical or cultural control of white mold, we hypothesized that these nurseries would represent the natural population of *S. sclerotiorum*.
Furthermore, as three cultivars (Beryl, Bunsi, and G122) were grown and tested previously by @otto-hanson2011variation among all white mold nurseries, we wanted to investigate the potential effect of cultivar on genetic diversity.
We additionally wanted to assess what categorical or phenotypic variables best predict genetic structure and if there was correlation between multilocus genotype and mycelial compatibility group.
By investigating these aims, we hope to effectively describe the population dynamics of *S. sclerotiorum* and make available our database of isolates for use in future dry bean breeding efforts.
